Growing libraries of concepts with wake-sleep program induction

### 2018-07-31 nips_2018_author_response.tex
small edits to response

\textbf{Choice of initial programming primitives:} Reviewer 1 observes that our initial set of programming primitives is
not as minimal as it could have been,
raising intriguing questions
about the importance and role of the initial basis.
We believe that general program-learners should not start with a \emph{minimal} basis,
but rather a \emph{domain-agnostic}
basis,
like those embodied in the standard libraries of modern programming languages.
An open question however is the extent to which one could ``learn from scratch.''
As a step toward answering this question,
we ran the following experiment:
SCC was provided with a minimal subset of primitives in 1959 Lisp, crucially including primitive recursion,
and tasked with solving a small set of functional programming exercises, like appending lists or summing the elements of a list.
After 93 hours on 64 CPUs,
SCC rediscovered \texttt{fold}, \texttt{unfold}, \texttt{map},
\texttt{length}, \texttt{zip}, \texttt{range}, \texttt{index},
and a handful of arithmetic operations.
Although this result is suggestive,
we believe that in practice learners should start from a rich yet domain-agnostic
inventory of primitives, like human programmers do.

@@

\textbf{Related Work:} We thank reviewer three for suggesting points of contact between our algorithm and other work in program induction.
We are revising our paper to prominently cite the work of Schmid and Kitzelmann,
whose \textsc{Igor} systems, like ours,
are motivated by the flexibility and generality of human learning.
Katayama's \textsc{MagicHaskeller} synthesizer for functional programs will also be cited.
More broadly,
we see these  related works as
 complementary to
our system:
we take a black-box synthesizer and
learn to use it by growing the DSL and
training a recognition model,
and one could replace our enumerative synthesizer with
\textsc{Igor}, Sketch (Solar-Lezama 2008), $\lambda^2$ (Feser et al. 2015), \textsc{MagicHaskeller},
genetic programming, or other synthesis algorithms.
We chose however to
use a generic and simple enumerative approach because it allowed us to apply SCC
to a diverse spread of problems: functional programming exercises, text editing,
turtle graphics programming, and symbolic regression from images.

>>>>

\textbf{Choice of initial programming primitives:} Reviewer 1 observes that our initial set of programming primitives is
not as minimal as it could have been,
raising intriguing questions
about the importance and role of the initial basis.
We believe that general program-learners should not start with a \emph{minimal} basis,
but rather a \emph{domain-agnostic}
basis,
like those embodied in the standard libraries of modern programming languages.
An open question however is the extent to which one could ``learn from scratch.''
As a step toward answering this question,
we ran the following experiment:
SCC was provided with a minimal subset of primitives in 1959 Lisp, crucially including primitive recursion,
and tasked with solving a moderate set of functional programming exercises, like appending lists or summing the elements of a list.
After 93 hours on 64 CPUs,
SCC rediscovered \texttt{fold}, \texttt{unfold}, \texttt{map},
\texttt{length}, \texttt{zip}, \texttt{range}, \texttt{index},
and a handful of arithmetic operations.
(We also tried the exact experiment Reviewer 1 suggests---removing only \texttt{length}---and confirmed that SCC rediscovers \texttt{length} when trained on our list processing domain.)
Although this result is suggestive,
we believe that in practice learners should start from a rich yet domain-agnostic
inventory of primitives, like human programmers do.

@@

\textbf{Related Work:} We thank reviewer three for suggesting points of contact between our algorithm and other work in program induction.
We are revising our paper to prominently cite the work of Schmid and Kitzelmann,
whose \textsc{Igor} systems, like ours,
are motivated by the flexibility and generality of human learning.
Katayama's \textsc{MagicHaskeller} synthesizer for functional programs will also be cited.
More broadly,
we see these  related works as
 complementary to
our system:
we take a black-box synthesizer and
learn to use it by growing the DSL and
training a recognition model,
and one could replace our enumerative synthesizer with
\textsc{Igor}, Sketch (Solar-Lezama 2008), \textsc{MagicHaskeller},
genetic programming, or other synthesis algorithms.
We chose however to
use a generic and simple enumerative approach because it allowed us to apply SCC
to a diverse spread of problems: functional programming exercises, text editing,
turtle graphics programming, and symbolic regression from images.
